A Survey of Exoskeleton Control (Draft 1.1)

### 2015-09-20 paper.tex
more updates

@@

Sensitivity Amplification Control (SAC) is a dynamic cancellation technique (a.k.a.
inverse dynamics, computed torque, or feedback linearization) that also tries
to adjust the apparent inertia of the exoskeleton (equation~\ref{eq:change-inertia1})

BLEEX:
Sensitivity amplification control (SAC) was
developed by Kazerooni [14]. In this method, the interaction
forces with the human are regarded as disturbances. The control
system has high sensitivity to disturbances and thus has fast
motion response to the interaction forces. The main drawback
of SAC is unwanted responses to any disturbance regardless of
being intentional or non-intentional disturbance. In addition,
highly accurate dynamic modelling is required in this
method.
\begin{verbatim}
H. Kazerooni, J.-L. Racine, L. Huang, and R. Steger, "On the control of
the berkeley lower extremity exoskeleton (BLEEX)," in Robotics and
Automation, 2005. ICRA 2005. Proceedings of the 2005 IEEE
International Conference on, 2005, pp. 4353-4360.
\end{verbatim}

@@

\newpage

\section{Appendix: Our List of Exoskeletons}

Please tell us what is missing.

\subsection{Surveys}

\begin{verbatim}
Surveys:
http://exoskeletonreport.com/
http://robohub.org/tag/exoskeleton/
http://robohub.org/exoskeletons-new-and-older/
http://neurogadget.com/tag/exoskeleton
http://www.engadget.com/tag/exoskeleton/
http://spectrum.ieee.org/robotics/medical-robots/exoskeletons-around-the-world
http://spectrum.ieee.org/robotics/medical-robots/exoskeletons-are-on-the-march
http://spectrum.ieee.org/biomedical/bionics/the-rise-of-the-body-bots
http://www.extremetech.com/electronics/139633-will-we-ever-have-iron-man-exoskeletons
http://futurewarstories.blogspot.com/2014/08/fws-topics-combat-exoskeletons.html
https://prezi.com/jygcvfxiesnm/a-brief-introduction-to-biomechanical-exoskeletons/
http://news.discovery.com/tech/robotics/exoskeleton-robots-top-5.htm
http://blog.equipoisinc.com/new-technologies-emerging-aerospace-defense-manufacturing/
http://nextbigfuture.com/2015/03/lower-body-exoskeleton-audi-chairless.html

H. Lee, W. Kim, J. Han, and C. Han, ”The technical trend of the
exoskeleton robot system for human power assistance, ” International
Journal of Precision Engineering and Manufacturing, vol. 13, pp. 1491-
1497, 2012.

E. Guizzo and H. Goldstein, "The rise of the body bots [robotic
exoskeletons]," Spectrum, IEEE, vol. 42, pp. 50-56, 2005.

A. M. Dollar, H. Herr, Lower extremity exoskeletons and active
orthoses: challenges and state-of-the-art, IEEE
Transactions on Robotics: 24 (2008) 144-158.
(surveys exoskeletons)
http://excedrin.media.mit.edu/wp-content/uploads/sites/3/2013/07/Dollar-2008_Lower-Extremity-Exoskeletons-and-Active-Orthoses-Challenges-and-State-of-the-Art.pdf

Simone Cinquemani Federico Casolo and Matteo Cocetta. On
active lower limb exoskeletons actuators. ISMA 08, 2008
\end{verbatim}

\subsection{Exoskeletons}

\begin{verbatim}
This is on the low end of the ballpark: 1.1m/s (4km/hr), 99lb (45kg) payload
IEEE 07222598
2015 IEEE International Conference on Advanced Intelligent Mechatronics (AIM)
July 7-11, 2015. Busan, Korea
Locomotion Control Strategy of Hydraulic Lower Extremity
Exoskeleton Robot
Hongchul Kim, Changhoon Seo, Young June Shin, Jung Kim, and Youn Sik Kang

BLEEX: Berkeley Lower Extremity Exoskeleton

Ekso Bionics
http://www.bloomberg.com/bw/articles/2013-03-28/businesses-bet-on-iron-man-like-exoskeletons

Sarcos XOS/WEAR
http://www.army-technology.com/features/featuremilitary-exoskeletons-uncovered-ironman-suits-a-concrete-possibility
http://www.robaid.com/bionics/raytheons-second-generation-exoskeleton-xos-2.htm
http://www.raytheon.com/newsroom/technology/rtn08_exoskeleton/
http://techcrunch.com/2010/09/27/sarcos-xos2-the-real-life-iron-man/
S. Jacobsen, ”On the development of XOS, a powerful exoskeletal
robot,” IEEEIRSJ IROS, Plenary Talk, 2007.

Lockheed Martin HULC, FORTIS
http://www.lockheedmartin.com/us/news/features/2014/mfc-103114-relief-daily-grind-industrial-exoskeletons-work.html
http://www.lockheedmartin.com/us/products/exoskeleton/FORTIS.html
http://www.dailytech.com/From+HULC+to+FORTIS+the+Evolution+of+Lockheed+Martins+Incredible+Exosuit/article36421.htm
http://www.wired.com/2014/09/navys-exoskeleton-could-make-workers-20-times-more-productive/
http://robrady.com/design-project/lockheed-martin-fortis-human-powered-exoskeleton
http://www.cnn.com/2013/05/22/tech/innovation/exoskeleton-robot-suit/

DKFI CAPIO and Exoskeleton Active (VI-Bot)
http://robotik.dfki-bremen.de/en/research/robot-systems/exoskeleton-passive.html
http://robotik.dfki-bremen.de/en/research/robot-systems/exoskeleton-active.html

DAEWOO
http://mashable.com/2014/08/05/daewoo-exoskeleton/#xz8IUKO3bmk_
http://www.geek.com/science/daewoo-dock-workers-now-using-strength-enhancing-exo-skeletons-1601290/

Vanderbilt
http://www.dailytech.com/Iron+Man+New+Robotic+Exoskeleton+Helps+Paraplegics+Walk/article29079.htm
http://research.vuse.vanderbilt.edu/cim/research_orthosis.html

Vanderbilt/Parker-Hannafin
http://www.indego.com/indego/en/home
https://www.youtube.com/watch?v=-bYYmZNxaZk
https://en.wikipedia.org/wiki/Vanderbilt_exoskeleton
http://www.roboticstrends.com/article/parker_hannifin_indego_exoskeleton
http://www.crainscleveland.com/article/20141112/BLOGS03/141119915/parker-hannifin-accepts-the-challenge-of-commercializing-the-indego--41951672-812546791-1442419256=:6352--

Activelink/Panasonic
http://pinktentacle.com/2009/09/power-loader-exoskeleton-suit/
http://www.extremetech.com/extreme/173463-worlds-first-affordable-powered-exoskeleton-is-almost-here-prepare-for-mech-wars
http://www.dealstreetasia.com/stories/panasonic-to-release-commercial-exoskeleton-to-market-in-4q-2015-9269/

Cyberdyne: HAL 2000 up to at least HAL 5
http://www.computerweekly.com/photostory/2240108388/Photos-Cyberdyne-Hal-robotic-exoskeleton-to-help-paralyzed/7/Japan-beats-the-US-to-it-Cyberdyne-Hal-robotic-exoskeleton-to-help-paralyzed
http://spectrum.ieee.org/robotics/medical-robots/exoskeletons-are-on-the-march
http://www.dailymail.co.uk/sciencetech/article-2384930/Robotic-exoskeleton-help-rehabilitate-disabled-people-passes-safety-tests--paving-way-sale-UK.html
H. Kawamoto, S. Lee, S. Kanbe, and Y. Sankai, "Power assist method
for HAL-3 using EMG-based feedback controller," in Systems, Man
and Cybernetics, 2003. IEEE International Conference on, 2003, pp.
1648-1653.

Noonee
http://www.extremetech.com/extreme/188417-rejoice-commuters-and-workers-the-chairless-chair-exoskeleton-lets-you-sit-down-anywhere-anytime

Kanagawa Institute of Technology
pneumatic exoskeleton developed at the Kanagawa Institute of Technology,
in Atsugi, Japan, allows Akiko Michihisa, a fitness trainer, ...
http://www.ubergizmo.com/2007/10/air-pressure-exoskeleton/

Monash/Chen
http://www.dailymail.co.uk/sciencetech/article-2639939/Super-fireman-The-hi-tech-exoskeleton-firefighters-superhuman-abilities.html
http://news.discovery.com/tech/robotics/firefighter-exoskeleton-to-the-rescue-140521.htm

Sagawa Electronics
https://www.youtube.com/watch?v=tYgHdxmCcAI
http://www.ohgizmo.com/2013/07/11/mk3-exoskeleton-suit-promises-to-make-schoolgirls-better-taller-stronger/
http://www.bitrebels.com/technology/powered-jacket-exoskeleton-japan/

Micromega
http://www.micromega-dynamics.com/esa-projects/exoskeleton.html

UCLA
http://bionics.seas.ucla.edu/research/exoskeleton_device_3.html
http://bionics.seas.ucla.edu/research/exoskeleton_device_2.html

RoboKnee
J. E. Pratt, B. T. Krupp, C. J. Morse, and S. H. Collins, "The
RoboKnee: an exoskeleton for enhancing strength and endurance
during walking," in Robotics and Automation, 2004. Proceedings.
ICRA'04. 2004 IEEE International Conference on, 2004, pp. 2430-
2435.

NASA/IHMC
http://www.nasa.gov/offices/oct/home/feature_exoskeleton.html#.VfHU72wVhBc
http://www.dailymail.co.uk/sciencetech/article-2216748/Nasa-developing-exoskeleton-help-astronauts-exercise-zero-gravity-help-disabled-people-walk-Earth.html
http://robots.ihmc.us/x1-mina-exoskeleton/

P.D. Neuhaus, et al., “Design and evaluation of Mina: A robotic
orthosis for paraple ics,” in Rehabilitation Robotics (ICORR), 2011
IEEE International Conference on. 2011. IEEE.

DARPA Warrior Web program
http://gajitz.com/darpas-exoskeleton-can-help-soldiers-run-4-minute-miles/
http://www.dailymail.co.uk/sciencetech/article-2348174/Robotic-exoskeleton--soft-light-pulls-like-pair-trousers--day-soldiers-superhuman-strength.html
http://www.theengineer.co.uk/in-depth/the-big-story/power-dressing-why-its-exoskeleton-time/1019633.articlehttp://www.theengineer.co.uk/in-depth/the-big-story/power-dressing-why-its-exoskeleton-time/1019633.article
http://www.engadget.com/2014/09/12/darpa-harvard-soft-exosuit/

ESA
http://www.esa.int/spaceinimages/Images/2014/06/Ready_to_wear_exoskeleton
http://www.esa.int/spaceinimages/Images/2014/06/Exoskeleton
http://www.sciencefocus.com/blog/exoskeleton-turning-man-machine

3D Systems
http://www.dezeen.com/2014/03/05/3d-printed-exoskeleton-helps-paralysed-users-walk/

U.Penn
http://www.popsci.com/article/technology/invention-awards-2014-powerful-portable-and-affordable-robotic-exoskeleton
https://www.youtube.com/watch?v=kAyI1YrWThQ

MIT Herr:
http://biomech.media.mit.edu/portfolio_page/load-bearing-exoskeleton-for-augmentation-of-human-running/

MIT exo
http://biomech.media.mit.edu/portfolio_page/load-bearing-exoskeleton-for-walking/
http://www.technovelgy.com/ct/Science-Fiction-News.asp?NewsNum=1205
C. J. Walsh, K. Endo, and H. Herr, "A quasi-passive leg exoskeleton
for load-carrying augmentation," International Journal of Humanoid
Robotics, vol. 4, pp. 487-506, 2007.

Honda (Stride Management Assist (SMA))
http://www.slashgear.com/honda-demo-walking-assist-exoskeleton-for-elderly-disabled-2211295/
http://singularityhub.com/2010/09/13/hondas-exoskeletons-help-you-walk-like-asimo-video/
Honda Walking Assist Device
Y. Ikeuchi, J. Ashihara, Y. Hiki, H. Kudoh, and T. Noda, "Walking
assist device with bodyweight support system," in Intelligent Robots
and Systems, 2009. IROS 2009. IEEE/RSJ International Conference on,
2009, pp. 4073-4079.

REX exoskeleton
http://www.rexbionics.com/
http://www.gizmag.com/rex-robotic-exoskeleton/15736/pictures
http://www.stripes.com/news/exoskeleton-could-benefit-troops-with-spinal-cord-injuries-1.113657
http://www.funis2cool.com/cool/rex-the-robotic-exoskeleton-could-change-the-lives-of-disabled-people.html

Waterloo
http://www.eng.uwaterloo.ca/~jpiorkow/fydp/

Soft pneumatic exo
http://cwwang.com/2008/04/08/soft-pneumatic-exoskeleton/

ReWalk
http://www.businessinsider.com/human-exoskeleton-approved-by-fda-2014-6

Revision Military PROWLER Human Augmentation System (HAS) Exoskeleton
https://www.youtube.com/watch?v=Zq4amM9u-6o

Yasakawa
http://www.crunchwear.com/yaskawa-electrics-ankle-exoskeleton-gives-strength/

http://www.engadget.com/2015/08/20/japans-top-oil-company-is-building-an-aliens-power-loader/

http://robohub.org/clinical-trials-begin-for-russias-first-medical-exoskeleton/

https://en.wikipedia.org/wiki/Z_series_(space_suits)

https://en.wikipedia.org/wiki/Extravehicular_Mobility_Unit

Passive:
http://techcrunch.com/2011/03/23/japanese-engineers-create-human-powered-exoskeleton-suit-video/
http://www.jneuroengrehab.com/content/6/1/21/figure/F2?highres=y

SUEFUL-7: A 7DOF upper-limb exoskeleton robot with muscle-model-oriented
EMG-based control
RARC Gopura, K Kiguchi, Y Li - Intelligent Robots and Systems …, 2009 -
ieeexplore.ieee.org

EU BALANCE program
http://balance-fp7.eu/
points us to European work
http://cordis.europa.eu/project/rcn/106854_en.html

MINDWALKER
key feature is actuation in lateral plane
http://www.3me.tudelft.nl/en/about-the-faculty/departments/biomechanical-engineering/research/dbl-delft-biorobotics-lab/exoskeleton/

https://mindwalker-project.eu/

http://www.utwente.nl/ctw/bw/research/projects/MINDWALKER/
http://tnsre.embs.org/2015/03/27/design-control-mindwalker-exoskeleton/

Each of the powered joints has a series elastic
actuator, which can deliver 100 Nm torque and 1 kW power -> 10rad/s
IEEE TRANSACTIONS ON NEURAL SYSTEMS AND REHABILITATION ENGINEERING, VOL. 23, NO. 2, MARCH 2015 277-
Design and Control of the MINDWALKER
Exoskeleton
Shiqian Wang, Letian Wang, Cory Meijneke, Edwin van Asseldonk, Thomas Hoellinger, Guy Cheron,
Yuri Ivanenko, Valentina La Scaleia, Francesca Sylos-Labini, Marco Molinari, Federica Tamburella,
Iolanda Pisotta, Freygardur Thorsteinsson, Michel Ilzkovitz, Jeremi Gancet, Yashodhan Nevatia,
Ralf Hauffe, Frank Zanow, and Herman van der Kooij

HEIKA
https://www.heika-research.de/26_166.php
HEiKA-EXO - Optimization-based development and control of an exoskeleton
for medical applications

http://www.beyondhd.tv/exoskeleton/

https://www.youtube.com/watch?t=3&v=myNRcDIgfjw
www.livescience.com/51940-mind-controlled-exoskeleton-robot.html
http://www.ibtimes.co.uk/scientists-develop-mind-controlled-robotic-exoskeleton-that-uses-leds-help-paraplegics-walk-1516834

http://csl-ep.mech.ntua.gr/index.php/research/telerobotics-and-servohydraulic-simulators/emg-exoskeleton-control

http://www.sarna.net/news/maxfas-exoskeleton-human-fire-control-supports-against-fatigue/
MAXFAS Exoskeleton: Human Fire Control Supports against Fatigue

Historical
Cornell Aeronautical Labs with funding from the US Air Force. This
resulted in the 1961-1962 Man-Amplifier suit that was more of an working
model than a working prototype.
The Cornell exo-suit was a mockup, and never included motors, servos, or
power.

GE's Hardiman I industrial exoskeleton project from 1965-1971 was the
first working exo-suit.
While a full mockup model was constructed, only pieces of Hardiman I
exo-suit worked, namely the claw-like arms. While the arms worked, the
leg-based frame work were an issue, especially with locomotion. By 1971,
GE canceled the project.
http://www.neatorama.com/2008/05/04/building-your-own-functional-iron-man-suit/

the best of the 1980's exo-suits was the 1988 NASA AX-5 Hardshell space
suit. For several decades, NASA's AMES had been working on a hadshelled
space suit system that they called the "AX" series. The apex of this
research was the 1988 AX-5.
While bulky, the AX-5 possessed 95% maneuverable of the naked human form,
and this suit was targeted for protection of astronauts in high-risk
areas. It was envisioned that the AX-5 would be used in EVAs in Earth
orbit and asteroid mining. In the end, it was determined that NASA did not
need a suit like this and alone with some remaining technical issues, the
AX hardsuits were shelved.
\end{verbatim}

\newpage

\section{Appendix: References To Be Processed}

Please suggest additional references.

\begin{verbatim}

Overviews ********************************

S.Viteckova, P.Kutilek, and M.Jirina, “Wearable Lower Limb Robotics:
A Review,” Biocybernetics and Biomedical Engineering, vol. 33, pp.
96–105, 2013.

”Lightening the Load”, U.S. Naval Research Advisory Committee
(NRAC), 2007.

Active Exoskeleton Control Systems: State of the Art
http://www.sciencedirect.com/science/article/pii/S1877705812026732

Control methodologies for upper limb exoskeleton robots
http://ieeexplore.ieee.org/xpl/login.jsp?tp=&arnumber=6427387&url=http%3A%2F%2Fieeexplore.ieee.org%2Fiel5%2F6416132%2F6426928%2F06427387.pdf%3Farnumber%3D6427387

A review of exoskeleton-type systems and their key technologies
CJ Yang, JF Zhang, Y Chen, YM Dong
http://pic.sagepub.com/content/222/8/1599.abstract

D. P. Ferris, “The exoskeletons are here,” Journal of Neuroengineering
and Rehabilitation, vol. 6, no. 17, pp. 1–3, 2009.

G. S. Sawicki and D. P. Ferris, “Mechanics and energetics of level
walking with powered ankle exoskeletons,” J. Exp. Biol., vol. 211, no.
Pt. 9, pp. 1402–1413, 2008.

http://www.bme.ncsu.edu/labs/hpl/SawickiDissertationFinal.pdf
Mechanics and energetics of walking with powered exoskeletons

Carry Payload *****************************

The first autonomously powered exoskeleton device that experimentally
demonstrated reduction in metabolic cost for human walking during
load carriage
L. M. Mooney, E. J. Rouse, and H. M. Herr, “Autonomous exoskeleton
reduces metabolic cost of human walking during load carriage,”
Journal of Neuroengineering and Rehabilitation, vol. 11, no. 80, 2014.

H. Kazerooni and R. Steger, “Berkeley lower extremity exoskeleton,”
ASME J. Dyn. Syst., Meas., Control, vol. 128, pp. 14–25, 2006.

C. J. Walsh, K. Pasch, and H. Herr, “An autonomous, underactuated
exoskeleton for load-carrying augmentation,” in Proc. IEEE/RSJ Int.
Conf. Intelligent Robots and Systems (IROS), 2006, pp. 4110–1415.

Impedance control **************************

G. A.-Ollinger, J. E. Colgate, M. A. Peshkin, and A. Goswami,
“Design of an active one-degree-of-freedom lower-limb exoskeleton
with inertia compensation,” Int. J. Robotics Research, vol. 30, no. 4,
pp. 486–499, 2011.

Learning ************************************

K. E. Gordon, C. R. Kinnaird, and D. P. Ferris, “Locomotor adaptation
to a soleus emg-controlled antagonistic exoskeleton,” J. Neurophysiol.,
vol. 109, no. 7, pp. 1804–1814, 2013.

EMG control ********************************

H. Kawamoto, S. Lee, S. Kanbe, and Y. Sankai, “Power assist method
for hal-3 using emg-based feedback controller,” in Proc. IEEE Int.
Conf. Syst., Man, Cybern., 2003, pp. 1648–1653.

S. Lee and Y. Sankai, “The natural frequency-based power assist
control for lower body with hal-3,” in Proc. IEEE Int. Conf. Sys. Man
Cyber. (ICSMC), 2003, pp. 1642–1647.

Not sorted ***********************************

master thesis design and control of a robotic exoskeleton for ...
digital.csic.es/.../Bortole_M_Design_Control_Robotic_Exoskeleton_Gait...
by M Bortole - ‎2013 - ‎Cited by 1
Control of a Robotic Exoskeleton for Gait Rehabilitation ” written by
Magdo Bortole as a requirement to obtain the Degree in the official Master
in Robotics and

Active Impedance:
A Novel Concept in Assistive Exoskeleton Control
http://www.ambarish.com/exos.html

http://gradworks.umi.com/33/86/3386362.html
Active impedance control of a lower-limb assistive exoskeleton
by Aguirre-Ollinger, Gabriel, Ph.D., NORTHWESTERN UNIVERSITY, 2009, 297
pages; 3386362

Active-impedance control of a lower-limb assistive exoskeleton
G Aguirre-Ollinger, JE Colgate… - … , 2007. ICORR 2007. …, 2007 -
ieeexplore.ieee.org

Design of an active one-degree-of-freedom lower-limb exoskeleton with
inertia compensation
G Aguirre-Ollinger, JE Colgate… - … Journal of Robotics …, 2011 -
ijr.sagepub.com

http://www.scholars.northwestern.edu/pubDetail.asp?t=pm&id=84856481679&
Inertia compensation control of a one-degree-of-freedom exoskeleton for
lower-limb assistance: Initial experiments

Power assist control for walking aid with HAL-3 based on EMG and impedance
adjustment around knee joint
S Lee, Y Sankai - Intelligent Robots and Systems, 2002. IEEE/ …, 2002 -
ieeexplore.ieee.org

http://www.intechopen.com/books/international_journal_of_advanced_robotic_syste\
ms/design-and-control-of-a-powered-hip-exoskeleton-for-walking-assistance
Design and Control of a Powered Hip Exoskeleton for Walking Assistance
By Qingcong Wu, Xingsong Wang, Fengpo Du and Xiaobo Zhang

http://www.jcomputers.us/vol9/jcp0901-29.pdf
Carrying Lower Extreme Exoskeleton Rapid
Terminal Sliding-Mode Robust Control

http://h2t.anthropomatik.kit.edu/pdf/Beil2015.pdf
Design and Control of the Lower Limb Exoskeleton KIT-EXO-1

Reducing the energy cost of human walking using an unpowered exoskeleton
http://www.nature.com/nature/journal/v522/n7555/fig_tab/nature14288_SF1.html

Control of a lower extremity exoskeleton for human performance
amplification
JLC Racine - 2003 - dl.acm.org

Locomotive control of a wearable lower exoskeleton for walking enhancement
KH Low, X Liu, CH Goh, H Yu - Journal of Vibration and Control, 2006 -
jvc.sagepub.com

Exoskeleton robots for upper-limb rehabilitation: state of the art and
future prospects
HS Lo, SQ Xie - Medical engineering & physics, 2012 - Elsevier

http://www.scielo.org.co/scielo.php?pid=S0123-30332014000100020&script=sci_arttext
Design and Implementation of a control strategy for static balance of a
lower limbs exoskeleton

Implementation of Real Time Control Algorithm for Gait ...
www.seipub.org/ABER/Download.aspx?ID=22038
Control approach follows gait trajectory using feedback sensors and
actuators for movement control. ... Exoskeleton Device; Real Time Control;
Gait Phases.

Exoskeleton control for lower-extremity assistance based on adaptive
frequency oscillators: Adaptation of muscle activation and movement
frequency
http://pih.sagepub.com/content/229/1/52.abstract

Control of a Lower Extremity Exoskeleton for Human ...
202.28.199.34/multim/3121656.pdf
The lower extremity exoskeleton is a wearable robotic device that should
... The control law makes use of dynamic models of the exoskeleton to
estimate the.

http://labrob.mty.itesm.mx/proyectos/robotic-exoskeletons
Robotic Exoskeletons

http://info.scichina.com/sciFe/EN/abstract/abstract516165.shtml
The relationship between physical human-exoskeleton interaction and
dynamic factors: using a learning approach for control applications

Online Assessment of Human-Robot Interaction for Hybrid Control of Walking
http://www.mdpi.com/1424-8220/12/1/215

\end{verbatim}

>>>>

BLEEX: carries
up to a 34 kg (75 lb) payload for the pilot and allows the pilot to
walk at up to 1.3 m/s (2.9 mph).

@@

Sensitivity Amplification Control (SAC) used to control BLEEX
is a dynamic cancellation technique (a.k.a.
inverse dynamics, computed torque, or feedback linearization) that also tries
to adjust the apparent inertia of the exoskeleton (equation~\ref{eq:change-inertia1})
using acceleration feedback. It is not clearly stated but it appears the
acceleration is the result of double differentiating position, as there do not
appear to be velocity sensors on BLEEX.

@@
